---
title: "HW4_566"
author: "Manda Abhinay Reddy"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

This is the unemployment data in US from 2010 to 2020. I got this data set from kaggle.

Through this data set I would like to compare the unemployment rates yearly based on several categories. I have explored the unemployment in US with respect to different races living in US, also unemployment among men and women.mFinally unemployment based on education.

I have grouped the data based on year and taken the average of the unemployment rates across various categories from years 2010 to 2020.

I have used packages such as kableExtra to create efficient tables and make the right interpretation. All the necessary formatting and styling are used accordingly. 

```{r}
library(tidyverse)
library(kableExtra)
unemp <- read.csv("unemployment_data_us.csv")
unemp <- unemp[complete.cases(unemp),]
head(unemp)

```

```{r}

unemp1 <- unemp %>%
  group_by(Year) %>%
    summarize(White = mean(White),
              Black = mean(Black),
              Asian = mean(Asian)
              )
kbl_unemp <- kbl(unemp1)
                    
kbl_unemp %>%
  kable_material(lightable_options = c("striped", "hover"))
```

```{r}
unemp2 <- unemp %>%
  group_by(Year) %>%
    summarize(Men = mean(Men),
              Women = mean(Women)
              )
#kbl_unemp1 <- kbl(unemp2)

kbl_unemp1 <- unemp2 %>% kbl(col.names = c("Year","Men","Women")) %>% add_header_above(c(" ", "Unemployment Rate among Men and Women"=2))

                    
kbl_unemp1 %>%
  kable_material(lightable_options = c("striped", "hover"))
```

```{r}
unemp3 <- unemp %>%
  group_by(Year) %>%
    summarize(Primary_School = mean(Primary_School),
              High_School = mean(High_School),
              Associates_Degree = mean(Associates_Degree),
              Professional_Degree = mean(Professional_Degree)
              )
kbl_unemp2 <- unemp3 %>% kbl(col.names = c("Year","Primary_School","High_School","Associates","Professional")) %>% add_header_above(c(" ","Unemployment Rate based on Education"=4))
                    
kbl_unemp2 %>%
  kable_material(lightable_options = c("striped", "hover"))
```

